BIOL424 Project Proposal

### 2021-08-20 proposal.tex
Add the question to the project proposal.
Add the hypotheses to the project proposal.

@@

>>>>

Do species form groups that are sufficiently similar in their interaction coefficients that they might be considered equivalent in parameterising a model?
If so, how?

@@

\begin{enumerate}
	\item There will be some grouping of species such that a Lotka--Volterra model will fit better when parameterised with that grouping than when parameterised entirely ungrouped.
	\item There will be no substantial benefit to model fit from grouping competitive effect and response separately, i.e. it will be sufficient to use the same groups for the rows as for the columns of the interaction matrix.
	\item Some grouping informed solely by phylogeny, at some taxonimic level or similar, will prove near-optimal among groupings.
\end{enumerate}
